Large Scale Marine Protected Areas

### 2019-01-22 docs/PIPA_Palau.tex
Deleted old rmd manuscript and updated tex file

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated English name is `Protected Area'.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. Countries that belong
to the PNA are shown in blue, while empty polygons indicates all others.
A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

For each vessel, we calculate total daily fishing hours and build a daily panel
with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
of vessels following a Before-After-Control-Impact (BACI) design, as well as the fishing hours, before
and after PIPA. Fig. \ref{fig:all_vessels} shows that mean fishing hours
for purse seiners have an abrupt increase, just before January 1st,
2015. This trend is observed for both treated and control groups. Across
all measures, the treatment and control vessels follow similar patterns,
confirming our claim that the control group provides a plausible
counterfactual. Figure \ref{fig:baci_strict} in the Appendix provides a visual
representation of the vessel-level fishing events that make up each
group through time. We use this panel data to answer our key research questions: 
Are the 61 purse seiners that used to fish within PIPA affected by the closure? If so, how?
What are they doing differently and where are they going that they didn't go to before?
The following section describes our empirical identification strategy.

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
\centering
\begin{tabular}[t]{lcccc}
\toprule
Group & n & Before & After & Change (A / B)\\
\midrule
Control & 26 & 11.74 & 20.13 & 1.71\\
Treatment & 61 & 10.67 & 18.36 & 1.72\\
\bottomrule
\end{tabular}
\end{table}

@@

Regression coefficients for our DiD analysis are shown in Table
\ref{tab:did}. Columns 1 -3 use our primary control group. Columns 4 - 6 use
only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
Columns 10 and 11 use Japanese vessels in the Pacific as controls, and
don't include flag fixed-effects to avoid perfect collinearity
between the Japanese flag and
control group status.
Our DiD analysis shows an overall increase in purse seine fishing hours,
even after accounting for the introduction of new satellites (Table
\ref{tab:did}).\footnote{Results of the same analysis is shown for longliners in Table \ref{tab:long}} This 
\emph{post} coefficient estimate is consistent across different
model specifications and across controls, and
effectively represents the patterns observed in Figure
\ref{fig:all_vessels}.

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
hours for all vessels in our main treatment-control groups. Solid
straight lines show a linear trend by period (pre-post) and treatment.
The other red and blue lines show monthly avarages. Vertical dashed
lines indicate dates when satellites were added, solid line indicates
PIPA closure.}
\end{figure}

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:did}Difference-in-differences estimates for 3 different controls and 3 different specifications. The first three columns use our primary control group. Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels. Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs. Numbers in parentheses are heteroskedasticity-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
\\[-1.8ex] & \multicolumn{11}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
 Constant & 6.345$^{***}$ & 7.863$^{***}$ & 10.322$^{***}$ & 7.124$^{***}$ & 9.007$^{***}$ & 9.933$^{***}$ & 6.057$^{***}$ & 7.584$^{***}$ & 10.194$^{***}$ & 22.625$^{***}$ & 24.731$^{***}$ \\ 
  & (0.186) & (0.274) & (0.404) & (0.265) & (0.341) & (0.620) & (0.193) & (0.279) & (0.538) & (0.629) & (0.683) \\ 
  & & & & & & & & & & & \\ 
 post & $-$0.052 & 1.134$^{***}$ & 1.115$^{***}$ & $-$1.199$^{***}$ & $-$0.279 & 0.124 & $-$0.284 & 1.013$^{***}$ & 1.166$^{***}$ & 2.330$^{***}$ & 3.991$^{***}$ \\ 
  & (0.303) & (0.304) & (0.339) & (0.435) & (0.429) & (0.436) & (0.318) & (0.318) & (0.357) & (0.890) & (0.877) \\ 
  & & & & & & & & & & & \\ 
 treated & $-$1.142$^{***}$ & $-$0.839$^{***}$ & 0.010 & $-$1.977$^{***}$ & $-$1.675$^{***}$ & 0.626 & $-$0.877$^{***}$ & $-$0.536$^{**}$ & 0.150 & $-$18.190$^{***}$ & $-$18.257$^{***}$ \\ 
  & (0.214) & (0.209) & (0.281) & (0.284) & (0.274) & (0.416) & (0.221) & (0.215) & (0.297) & (0.673) & (0.661) \\ 
  & & & & & & & & & & & \\ 
 sate2 & 12.579$^{***}$ & 11.589$^{***}$ & 11.340$^{***}$ & 12.709$^{***}$ & 11.850$^{***}$ & 11.749$^{***}$ & 12.631$^{***}$ & 11.599$^{***}$ & 11.349$^{***}$ & 14.346$^{***}$ & 12.967$^{***}$ \\ 
  & (0.197) & (0.199) & (0.232) & (0.212) & (0.213) & (0.246) & (0.199) & (0.201) & (0.235) & (0.303) & (0.309) \\ 
  & & & & & & & & & & & \\ 
 sate3 & 14.675$^{***}$ & 13.587$^{***}$ & 13.328$^{***}$ & 14.799$^{***}$ & 13.894$^{***}$ & 13.795$^{***}$ & 14.958$^{***}$ & 13.804$^{***}$ & 13.566$^{***}$ & 15.187$^{***}$ & 13.719$^{***}$ \\ 
  & (0.260) & (0.262) & (0.307) & (0.286) & (0.287) & (0.329) & (0.264) & (0.266) & (0.315) & (0.402) & (0.410) \\ 
  & & & & & & & & & & & \\ 
 post:treated & $-$0.515$^{*}$ & $-$0.833$^{***}$ & $-$0.934$^{***}$ & 0.562 & 0.373 & $-$0.176 & $-$0.439 & $-$0.814$^{***}$ & $-$1.084$^{***}$ & $-$3.209$^{***}$ & $-$3.715$^{***}$ \\ 
  & (0.281) & (0.276) & (0.310) & (0.413) & (0.402) & (0.407) & (0.293) & (0.287) & (0.326) & (0.811) & (0.799) \\ 
  & & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Control & All & All & All & PNA & PNA & PNA & -CHN & -CHN & -CHN & JPN & JPN \\ 
Month FE & No & Yes & Yes & No & Yes & Yes & No & Yes & Yes & No & Yes \\ 
Flag FE & No & No & Yes & No & No & Yes & No & No & Yes & No & No \\ 
Observations & 37,840 & 37,840 & 30,359 & 30,583 & 30,583 & 25,034 & 36,415 & 36,415 & 28,934 & 34,047 & 34,047 \\ 
R$^{2}$ & 0.171 & 0.200 & 0.208 & 0.178 & 0.208 & 0.215 & 0.173 & 0.203 & 0.211 & 0.260 & 0.280 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{11}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
		number of vessels by month for all vessels. Vertical dashed lines
		indicates dates when satellites were added, solid line indicates PIPA
		closurePIPA closure.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{img/LSMPAs_map.pdf}
\caption{\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated English name is `Protected Area'.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{img/PNA_map.pdf}
\caption{\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. Countries that belong
to the PNA are shown in blue, while empty polygons indicates all others.
A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

For each vessel, we calculate total daily fishing hours and build a daily panel
with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
of vessels following a Before-After-Control-Impact (BACI) design, as well as the fishing hours, before
and after PIPA. Fig. \ref{fig:all_panels} shows that mean fishing hours
for purse seiners have an abrupt increase, just before January 1st,
2015. This trend is observed for both treated and control groups. Across
all measures, the treatment and control vessels follow similar patterns,
confirming our claim that the control group provides a plausible
counterfactual. Figure \ref{fig:baci_strict} in the Appendix provides a visual
representation of the vessel-level fishing events that make up each
group through time. We use this panel data to answer our key research questions: 
Are the 61 purse seiners that used to fish within PIPA affected by the closure? If so, how?
What are they doing differently and where are they going that they didn't go to before?
The following section describes our empirical identification strategy.

\input{tab/baci_n_s}

@@

Regression coefficients for our DiD analysis are shown in Table
\ref{tab:did}. Columns 1 -3 use our primary control group. Columns 4 - 6 use
only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
Columns 10 and 11 use Japanese vessels in the Pacific as controls, and
don't include flag fixed-effects to avoid perfect collinearity
between the Japanese flag and
control group status.
Our DiD analysis shows an overall increase in purse seine fishing hours,
even after accounting for the introduction of new satellites (Table
\ref{tab:did}).\footnote{Results of the same analysis is shown for longliners in Table \ref{tab:long}} This 
\emph{post} coefficient estimate is consistent across different
model specifications and across controls, and
effectively represents the patterns observed in Figure
\ref{fig:all_panels}.

@@

\begin{figure}
\centering
\includegraphics{img/all_panels.pdf}
\caption{\label{fig:all_panels}Time seri showing mean monthly values es for our 10 variables of interest:
A) Fishing hours, B)Non-fishing hours at-sea,
C) Proportion of fishing hours to total hours at-sea,
D) Distance traveled, E) Mean distance from port,
F) Mean distance from shore,
G) Mean distance from port for fishing events,
H) Mean distance from shore for fishing events,
I) Proportion of hours spent in Kiribati waters,
J) Proportion of fishing hours spent in PNA waters.}
\end{figure}

@@

\input{tab/main_DID}

@@

\begin{figure}
	\centering
	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
		number of vessels by month for all vessels. Vertical dashed lines
		indicates dates when satellites were added, solid line indicates PIPA
		closurePIPA closure.}
\end{figure}
